### 2016-11-04 introduction.tex
more shit

\section{Introduction \& Literature Review}\label{sec1}
Pruning algorithms, as comprehensively surveyed by \cite{reed1993pruning}, are a useful set of heuristics designed to identify and remove network elements which do not contribute significantly to the output of the network and potentially inhibit generalization performance. This is motivated by the well-known tendency of neural networks to over-fit to the idiosyncrasies of their training data when given too many parameters or too few input patterns from which to generalize.

Neural network pruning algorithms were first popularized by \cite{sietsma1988neural} as a mechanism to determine the proper size of a network required to solve a particular problem. To this day, network design and optimal pruning remain inherently difficult tasks. For problems which cannot be solved using linear threshold units alone, \cite{baum1989size} demonstrate there is no way to precisely determine the appropriate size of a neural network a priori given any random set of training instances. Using too few neurons inhibits learning, and so in practice it is common to attempt to over-parameterize networks initially using a large number of hidden units and weights. However, as \cite{chauvin1990generalization} writes, this approach can lead to over-fitting as the network's unnecessary free parameters start to latch on to idiosyncrasies in the training data.

%\section{Related Work}

The generalization performance of neural networks has been well studied, and apart from pruning algorithms many heuristics have been used to avoid overfitting, such as dropout (\cite{srivastava2014dropout}), maxout (\cite{goodfellow2013maxout}), and cascade correlation (\cite{fahlman1989cascade}), among others. However, these algorithms do not explicitly prioritize the reduction of network memory footprint as a part of their optimization criteria per se, (although in the opinion of the authors, Fahlman's cascade correlation architecture holds great promise in this regard.) Computer memory size and processing capabilities have improved so much since the introduction of pruning algorithms in the late 1980s that space complexity has become a relatively negligible concern. The proliferation of cloud-based computing services has furthermore enabled mobile and embedded devices to leverage the power of massive data and computing centers remotely. In this domain, however, it is also reasonable to suggest that certain performance-critical applications running on low-resource devices could benefit from the ability to use neural networks locally.

At present there are few (if any) mechanisms specifically designed to shrink neural networks down in order to meet an externally imposed constraint on byte-size in memory. Without explicitly removing parameters from the network, one could use weight quantization to reduce the number of bytes used to represent each weight parameter, as investigated by \cite{balzer1991weight}, \cite{dundar1994effects}, and \cite{hoehfeld1992learning}. Of course, this method can only reduce the size of the network by a factor proportional to the byte-size reduction of each weight parameter.

Recently, some other network compression methods have been proposed. One such method which has recently gained popularity (\cite{prabhavalkar2016svd}) uses the singular values of a trained weight matrix as basis vectors from which to derive a compressed hidden layer. Some other recent works like \cite{Anders2016quant} have tried successfully to achieve compression through weight quantization followed by encoding while some others like \cite{deepcompression2016} have tried to build on top of that by adding weight-pruning as a preceding step to quantization and encoding.

>>>>

\section{Introduction \& Literature Review}\label{sec1}
Pruning algorithms, as comprehensively surveyed by \cite{reed1993pruning}, are a useful set of heuristics designed to identify and remove elements from a neural network which are either redundant or do not significantly contribute to the output of the network. This is motivated by the observed tendency of neural networks to over-fit to the idiosyncrasies of their training data given too many trainable parameters or too few input patterns from which to generalize, as stated by \cite{chauvin1990generalization}.

Network architecture design and hyperparameter selection are inherently difficult tasks typically approached using a few well-known rules of thumb, e.g. various weight initialization procedures, choosing the width and number of layers, different activation functions, learning rates, momentum, etc. Some of this ``black art'' appears unavoidable. For problems which cannot be solved using linear threshold units alone, \cite{baum1989size} demonstrate that there is no way to precisely determine the appropriate size of a neural network a priori given any random set of training instances. Using too few neurons seems to inhibit learning, and so in practice it is common to attempt to over-parameterize networks initially using a large number of hidden units and weights, and then prune them afterwards if necessary.

The generalization performance of neural networks has been well studied, and apart from pruning algorithms many heuristics have been used to avoid overfitting, such as dropout (\cite{srivastava2014dropout}), maxout (\cite{goodfellow2013maxout}), and cascade correlation (\cite{fahlman1989cascade}), among others. Compressing networks often has benefits with respect to generalization performance and the portability of neural networks to operate in memory-constrained or embedded environments. Without explicitly removing parameters from the network, weight quantization allows for a reduction in the number of bytes used to represent each weight parameter, as investigated by \cite{balzer1991weight}, \cite{dundar1994effects}, and \cite{hoehfeld1992learning}.

A recently proposed method for compressing recurrent neural networks (\cite{prabhavalkar2016compression}) uses the singular values of a trained weight matrix as basis vectors from which to derive a compressed hidden layer. Some other recent works like \cite{Anders2016quant} have tried successfully to achieve compression through weight quantization followed by an encoding step while others such as \cite{deepcompression2016} have tried to expand on this by adding weight-pruning as a preceding step to quantization and encoding.

\section{Review of Pruning Algorithms}
